stupid backoff

### 2019-12-02 al_stup.Rmd
presentation

getTrigProbs = function(bigPre, trigrams, bigrams, unigrams) {
        obs_trigs = getODTrigs(bigPre, trigrams)
        regex = sprintf("%s%s%s", "^", bigPre, "$")
        #bigr_count = bigrams[grep(regex, bigrams$ngram), ]$freq
        bigr_count = bigrams[ngram %like% regex]$freq

        if(nrow(obs_trigs) < 1) {
                bigr_probs = getBigProbs(bigPre, bigrams, unigrams)
                probs = data.table(ngram = bigr_probs$ngram, 
                                   prob = bigr_probs$prob * 0.4)
                return(probs)
        } else {
                probs = obs_trigs %>% rename( prob = freq) %>%
                    mutate(prob = prob / bigr_count) %>% 
                    arrange(desc(prob), ngram)
                return(probs)
        }

@@

getBigProbs = function(bigPre, bigrams, unigrams) {
    obs_bigs = getODBigs(bigPre, bigrams)
    w_i_1 <- str_split(bigPre, "_")[[1]][2]
    regex = sprintf("%s%s%s", "^", w_i_1, "$")
    #unig_count = unigrams[grep(regex, unigrams$ngram), ]$freq
    unig_count = unigrams[ngram %like% regex]$freq
    if(nrow(obs_bigs) < 1) {
        probs = getUnigProbs(unigrams) %>% mutate(prob = prob * 0.4)
        return(probs)
    } else {
        probs = obs_bigs %>% rename(prob = freq) %>%
            mutate(prob = prob/unig_count) %>%
            arrange(desc(prob), ngram)
        return(probs)
    }
}

>>>>

getTrigProbs = function(bigPre, trigrams, bigrams, unigrams) {
        obs_trigs = getODTrigs(bigPre, trigrams)
        regex = sprintf("%s%s%s", "^", bigPre, "$")
        #bigr_count = bigrams[grep(regex, bigrams$ngram), ]$freq
        bigr_count = bigrams[ngram %like% regex]$freq
        count = length(strsplit(bigPre, "_")[[1]])
        if(count < 2 | nrow(obs_trigs) < 1) {
                bigr_probs = getBigProbs(bigPre, bigrams, unigrams)
                probs = data.table(ngram = bigr_probs$ngram, 
                                   prob = bigr_probs$prob * 0.4)
                return(probs)
        } else {
                probs = obs_trigs %>% rename( prob = freq) %>%
                    mutate(prob = prob / bigr_count) %>% 
                    arrange(desc(prob), ngram)
                return(probs)
        }

@@

getBigProbs = function(bigPre, bigrams, unigrams) {
    obs_bigs = getODBigs(bigPre, bigrams)
    w_i_1 <- str_split(bigPre, "_")[[1]][2]
    regex = sprintf("%s%s%s", "^", w_i_1, "$")
    #unig_count = unigrams[grep(regex, unigrams$ngram), ]$freq
    unig_count = unigrams[ngram %like% regex]$freq
    if(nrow(obs_bigs) < 1) {
        probs = getUnigProbs(unigrams) %>% mutate(prob = freq * 0.4)
        return(probs)
    } else {
        probs = obs_bigs %>% rename(prob = freq) %>%
            mutate(prob = prob/unig_count) %>%
            arrange(desc(prob), ngram)
        return(probs)
    }
}
